---
title: "Elite Trump Donors From Texas"
author: "Stephen Neukam"
date: "`r Sys.Date()`"
title-block-banner: true
format:
  html:
    #theme: cosmo
    layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  echo: false
  warning: false
  message: false
---

```{css}

.small-grey-text {
   font-size: .7em; 
   color: Gray
}

```

```{r}
#| label: load_libraries_settings_functions_data
#| include: false

###
# Load libraries
###
library(tidyverse)
library(janitor)
library(data.table)
library(rmarkdown)

devtools::install_github("kent37/summarywidget")

pacman::p_load(tidyverse, crosstalk, DT, lubridate, plotly, reactable, gt, summarywidget, here, glue, janitor, googlesheets4, googledrive, ggthemes, devtools, knitr, kableExtra,tidytext,textstem)

output_formatted_table = function(table, text, label_text = NULL){
  
  table %>%
    kable(caption = text, label = label_text) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 14, fixed_thead = T) %>%
    scroll_box(width = "100%")
}
###
# Load data
###
maga_pac <- read_csv("data/maga_pac.csv") %>%
  select(-committee_id, -report_type:-entity_type, -unused_contbr_id:-recipient_committee_designation, -contributor_id:-memo_code_full, -contributor_aggregate_ytd:-conduit_committee_id, -conduit_committee_name:-line_number_label) %>%
  clean_names() %>%
  mutate(contributor_zip = as.numeric(contributor_zip))
save_america_pac <- read_csv("data/save_america_pac.csv") %>%
  select(-committee_id, -report_type:-entity_type, -unused_contbr_id:-recipient_committee_designation, -contributor_id:-memo_code_full, -contributor_aggregate_ytd:-conduit_committee_id, -conduit_committee_name:-line_number_label) %>%
  clean_names()
trump_victory <- read_csv("data/trump_victory.csv") %>%
  select(-committee_id, -report_type:-entity_type, -unused_contbr_id:-recipient_committee_designation, -contributor_id:-memo_code_full, -contributor_aggregate_ytd:-conduit_committee_id, -conduit_committee_name:-line_number_label) %>%
  clean_names()

### Merging these two datasets into one master dataset
master <- maga_pac %>%
  bind_rows(save_america_pac, trump_victory)
###
# Making a full name column
###
master <- master %>%
  mutate(full_name = paste0(contributor_first_name, " ", contributor_last_name))

### Who donated the most to Trump from Texas?
top_donors <- master %>%
  group_by(full_name, contributor_city) %>%
  summarise(total = sum(contribution_receipt_amount)) %>%
  arrange(desc(total))

###
# Filter top donors by donors who contributed more than $10,000
###
elite_donors <- top_donors %>%
  filter(total > 9999) %>%
  filter(full_name != "NA NA")

###
# Searchable, filterable and sortable table
###

# Remove columnDefs if you don't want to hide any columns
elite_donors_table <- elite_donors |> 
  datatable(   
    filter = "top", 
    extensions = c(
      "Buttons"
    ), 
    rownames=FALSE,
    escape=FALSE,
    #    style="bootstrap", 
    class="compact cell-border stripe", 
    width="100%"
      )

### 
# Trump donors over 100k
###
over_100k <- elite_donors %>%
  filter(total > 99999)
```
## Mega Trump donors from Texas
There are `r nrow(elite_donors)` donors from Texas who contributed over $10,000 to Donald Trump in the past. These donors have helped fuel a variety of his super PACs and campaign committees. There are `r nrow(over_100k)` donors from Texas who contributed at least $100,000 to the former president. A searchable and filterable table of those donors is below.

### Table of elite Trump donors from Texas
```{r}
elite_donors_table
```

